### 2021-06-07 paper/report.tex
Fix graph, error, add citation.

We apply this model to Germany. In March and April 2020, the country broke the first wave
of the pandemic fairly quickly. Between mid-May and mid-September, daily new infections
were below 20 per Million and day.\comment[id=HM]{Cite our world in data} We model the
period mid-September 2020 to the end of May 2020. We pick the starting date for two
reasons. First, we do not include the first wave because the environment was very
different (e.g., aggregate PCR test capacity was much lower and we would require a very
different model for calculating the share of known cases) and some data was not recorded
yet.\comment[id=HM]{True?}\comment[id=K]{We would definitely need to model national
and international travel which you mention below. Regarding data I think everything would
be available. The low numbers during summer in our sample size might also be a problem
because Covid might go extinct in our model when case numbers are so low.}. Second, a
large fraction cases during summer of 2020 were traced to international
travel,\comment[id=HM]{citation?}\comment[id=Klara]{There was a comment by minister Spahn
that half of cases during the summer months were due to travel to the Baltic
(\url{https://twitter.com/krstorevic/status/1396516025181556737}) but I know of no data.
We should probably check the RKI reports of July, Aug and Sep}, but the precise number is difficult to model.

@@

        \caption{{\small Tests and vaccinations}}
        \label{fig:antigen_tests_vaccinations}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/testing/assumed_overall_share_known_cases}

>>>>

We apply this model to Germany. In March and April 2020, the country broke the first wave
of the pandemic fairly quickly. Between mid-May and mid-September, daily new infections
were below 20 per Million and day.\comment[id=HM]{Cite our world in data} We model the
period mid-September 2020 to the end of May 2020. We pick the starting date for two
reasons. First, we do not include the first wave because the environment was very
different (e.g., aggregate PCR test capacity was much lower and we would require a very
different model for calculating the share of known cases) and some data was not recorded
yet.\comment[id=HM]{True?}\comment[id=K]{We would definitely need to model national
and international travel which you mention below. Regarding data I think everything would
be available. The low numbers during summer in our sample size might also be a problem
because Covid might go extinct in our model when case numbers are so low.}. Second, a
large fraction cases during summer of 2020 were traced to international
travel,\comment[id=HM]{cite \url{https://www.rki.de/DE/Content/Infekt/EpidBull/Archiv/2021/Ausgaben/08_21.pdf}}, but the precise number is difficult to model.

@@

        \caption{{\small Tests and vaccinations}}
        \label{fig:antigen_tests_vaccinations}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/share_of_b117_acc_to_rki}
